{\it E}nKCF: Ensemble of Kernelized Correlation Filters for Object Tracking in High Speed

### 2017-04-26 old_draft.tex
Cleaning up and re-structuring the intro.

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}
% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical application of embedded systems in that most of the embedded systems already includes image acquisition pipeline and a tremendous amount of progresses on research has been made. However, to successfully deploy a computer vision algorithm on any existing embedded systems, a vision algorithm needs to satisfy some criteria: minimal, manual intervention after deployment and small footprint of computing resource consumption and executable size. This criteria assumes the performance of the algorithm is reasonably good. To this end, in this paper, we propose an ensemble of the kernelized correlation filters (KCF), aka EnKCF, for a single-target object tracking. In particular, we developed a
committee of KCFs to specifically address the scale-change and the translation over frames in an independent manner. Scale and translation tasks are distributed to this group of KCFs in a way to keep the frame rate per second as high as a single naive KCF tracker without scale adaptation module. In addition, we devised a Bayes filter to minimize the gap of interactions between KCFs. It is well known that an online, model-free tracker like ours is prone to drift over time. To cope with such drifts, we developed a re-detection module that reliably identifies when to lose the target, hand-picks a small number of object proposals from existing object proposal methods (e.g., "Edge Box"), and re-initializes the track to track the object for a longer period. The proposed EnKCF tracker also leads to a more robust re-detection module then a naive KCF as it includes target-only area scale filter and target+background area translation filters with different feature modalities which can be used to search for the target box among the object proposals. To verify the usefulness of the proposed method, we compared the performance of ours to those of existing other online high speed tracking methods. Experimental results showed that the performance of our tracker are $72.53\%$ precision at $20$ px, $52.90\%$ area under the success curve (AUC) for OTB100 data and $55.71\%$ and $41.71\%$ for UAV123 data. This confirmed that our tracker outperformed the existing high speed correlation filter based trackers about $5\%$ in precision at $20$ px and $10\%$-$20\%$ in AUC. These numbers also compete well with other scale adaptive lower speed trackers such as SAMF, DSST, and Struct. Finally, our implementation ran at $340$ fps for OTB100 dataset and at $416$ fps for UAV123 dataset that is as fast as other correlation filter based trackers such as KCF ($292$ fps), DCF($457$ fps) and STC ($350$ fps) for UAV123.
\end{abstract}

@@

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because those mobile platforms have limited payload to carry other
active sensors and, without increasing much cost, installation of a
monocular camera even stereo rigs would increase the usefulness of a
mobile platform. For example, instead of just bare flight function
with video recording, an unmanned air vehicle (UAV) equipped with
object or feature following would make it more useful in the
application of monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

{\it YoungWoo: Need to clean up the following paragraphs until Section
  2.}

The tracking-by-detection methods have recently used extensively as a
robust, powerful, and highly discriminative vision-based, object
tracking method replacing the preceding, generative object tracking
methods that primarily concerned about learning the appearance of the
target.

@@

{\it YoungWoo : They are not related at all, however, I wanted to give a brief idea about tracking-by-detection challenges. I feel like the text in between line 147 - 187 can precede the paragraph starting at line 122. Do you think it makes sense? This way, we give an introduction on tracking-by-detection.}

@@

An object tracking method based on the correlation filter in frequency
domain has gained attention due to its fast computation.

@@

{\it YoungWoo : I think the following paragraph and paragraph in between line 118-143 give a brief idea about CF and KCF. We can probably combine them in a single paragraph followed by our contributions.}

The first correlation filter tracker proposed by
\cite{bolme2010visual} focused on learning and detection in the
frequency domain. The idea was to minimize the sum of squared error in
the frequency domain. Hence, the convolution in the original domain is
avoided, instead, element-wise multiplication is needed in the
frequency domain. This way, it achieved promising performance at 700
Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
changing background as it learns the filter using a single template
and accommodates single channel features. Later on, the MOSSE tracker
was improved by using the circularly shifted background patches in an
efficient way by utilizing the theorem that Discrete Fourier Transform
of a circulant matrix gives us diagonalized circulant matrix
\cite{henriques2012exploiting,henriques2015high}. In the same work,
the authors integrated kernelization concept into the detection and
learning steps to improve tracking
accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
correlation filter trackers with single channel features to
multi-channel features. They employed the color and shape features in
a simple framework by summing the correlation of the test and learned
feature channels elements. There a few major drawbacks of the
correlation filter trackers although they outperformed the other
discriminative trackers with superior computation. First, due to the
nature of correlation filters it is limited to a region of interest
which is typically 2-3 times larger than the target. Considering a
larger ROI not only increases the computational burden but also leads
to further spatial information loss with the fixed template size. For
this reason, its performance degrades in fast motion cases as the ROI
may not contain the target. Second, the correlation filter lacks scale
adaptation ability since it only estimates the translation of the
target. Later studies focused on improving the latter issue by
proposing scale candidates where each scale is assigned a confidence
by performing detection on the shrinked or enlarged the ROI
\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
group of studies employ the part-based correlation filter trackers to
better adapt to the scale changes
\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
is generally handled in the long-term target tracking framework where
track reinilization module is triggered when the target is lost
\cite{ma2015long,de2015board,li2016monocular}.

@@

\begin{figure}[!t]
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters denoted as \textit{target+small background} translation filter,
  \textit{target-only} scale filter and \textit{target+large background} translation filters are
  shown. Also, the hanning window and desired Gaussian response for
  each filter is displayed.}
\label{fig:Filters}
\end{figure}

@@

\begin{algorithm}
	\caption{The EnKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n = 5$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=2$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n=1\:\:or\:\:fc\:\%\:n=4$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1), 
		         \State Skip it for $R_{t}^{L}$ (Condition 1),
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$;
				\State // Update Translation
				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$PSR(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$PSR(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran our algorithm using
two publicly available datasets:
%VOT2015 \footnote{\url{http://www.votchallenge.net/}},
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}. OTB100 dataset contains video sequences for 100 objects whereas UAV123 dataset contains aerial footage of 123 objects. The proposed $EnKCF$ method can better handle slow motions. Also, the UAVs use mobiles platforms with limited computational power. We believe that the proposed tracker can better fit for tracking from such platforms as it is highly efficient and scale adaptive. Taking into account these reasons, it is more appropriate to test it on aerial videos captured by UAVs.

We compare the proposed tracker to other state-of-the-art high speed trackers using the \textit{Precision} and \textit{Success} metrics. Precision is computed as the eucl%

>>>>

% If you comment hyperref and then uncomment it, you should delete
% egpaper.aux before re-running latex.  (Or just hit 'q' on the first latex
% run, let it finish, and you should be clear).
\usepackage[pagebackref=true,breaklinks=true,letterpaper=true,colorlinks,bookmarks=false]{hyperref}

% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

%%%%%%%%% ABSTRACT
\begin{abstract}
Computer vision technologies are very attractive for practical
applications for embedded systems in that most of the embedded systems
already includes image acquisition pipeline and a tremendous amount of
progresses on research has been made for many areas. However, to
successfully deploy a computer vision algorithm on any existing
embedded systems, a vision algorithm needs to satisfy some criteria:
minimal, manual intervention after deployment and small footprint of
computing resource consumption and on executable code, with the
assumption of reasonably good performance. To this end, in this paper,
we propose an ensemble of the kernelized correlation filters (KCF), we
call {\it E}nKCF, for a single-target object tracking. In particular,
we developed a committee of KCFs to specifically address the
scale-change and dynamic maneuver of the target over frames. In
addition, we devised a Bayes filter for a smooth transition between
individual KCFs' executions. To minimize the effect of drifting, we
also developed another algorithm that detects target-lost, uses an
existing object proposal method (e.g., ``Edge Box'') to re-detect the
lost target, and re-initializes the previous tracking for a long-term
tracking. To verify the usefulness of the proposed method, we compared
the performance of ours to those of the existing online tracking
methods. Experimental results showed that the performance of ours are
72.53\% for precision on 20 pixels and 52.90\% for success rate for
OTB100 data, and 55.71\% and 41.71\% for UAV123 data. These results
confirmed that our method outperformed the existing ones over 5\% on
precision on 20 pixels and 10-20\% on AUC on average. Our
implementation ran at 340 fps for OTB100 and at 416 fps for UAV123
data that is faster than DCF (292 fps) for OTB100 and KCF (292 fps),
DCF (457 fps), and STC (350 fps) for UAV123.
\end{abstract}

@@

A recent proliferation of air/ground/water unmanned vehicle
technologies has ever increased interests on deployment of intelligent
algorithms on embedded or mobile platforms. Among those technologies,
computer vision algorithms are getting more attentions primarily
because those mobile platforms have limited payload to carry other
active sensors than a lightweight, monocular camera and, without
increasing much cost, installation of a monocular camera even stereo
rigs would increase the usefulness of a mobile platform. For example,
instead of having just bare flight function with video recording, an
unmanned air vehicle (UAV) equipped with object or feature following
would make it more useful in the application of
monitoring/surveillance/surveying on private
properties/wild-life/crop, video recording on sports/movies/events,
many others.

@@

\begin{comment}
The tracking-by-detection methods have recently used extensively as a
robust, powerful, and highly discriminative vision-based, object
tracking method replacing the preceding, generative object tracking
methods that primarily concerned about learning the appearance of the
target.

@@

{\it YoungWoo : They are not related at all, however, I wanted to give a brief idea about tracking-by-detection challenges. I feel like the text in between line 147 - 187 can precede the paragraph starting at line 122. Do you think it makes sense? This way, we give an introduction on tracking-by-detection.}
\end{comment}

@@

@@

\begin{comment}
The first correlation filter tracker proposed by
\cite{bolme2010visual} focused on learning and detection in the
frequency domain. The idea was to minimize the sum of squared error in
the frequency domain. Hence, the convolution in the original domain is
avoided, instead, element-wise multiplication is needed in the
frequency domain. This way, it achieved promising performance at 700
Hz. On the other hand, the MOSSE tracker failed in cases with rapidly
changing background as it learns the filter using a single template
and accommodates single channel features. Later on, the MOSSE tracker
was improved by using the circularly shifted background patches in an
efficient way by utilizing the theorem that Discrete Fourier Transform
of a circulant matrix gives us diagonalized circulant matrix
\cite{henriques2012exploiting,henriques2015high}. In the same work,
the authors integrated kernelization concept into the detection and
learning steps to improve tracking
accuracy. \cite{galoogahi2013multi,henriques2015high} extended the
correlation filter trackers with single channel features to
multi-channel features. They employed the color and shape features in
a simple framework by summing the correlation of the test and learned
feature channels elements. There a few major drawbacks of the
correlation filter trackers although they outperformed the other
discriminative trackers with superior computation. First, due to the
nature of correlation filters it is limited to a region of interest
which is typically 2-3 times larger than the target. Considering a
larger ROI not only increases the computational burden but also leads
to further spatial information loss with the fixed template size. For
this reason, its performance degrades in fast motion cases as the ROI
may not contain the target. Second, the correlation filter lacks scale
adaptation ability since it only estimates the translation of the
target. Later studies focused on improving the latter issue by
proposing scale candidates where each scale is assigned a confidence
by performing detection on the shrinked or enlarged the ROI
\cite{li2014scale,tang2015multi,bibi2015multi,ma2015long}. Another
group of studies employ the part-based correlation filter trackers to
better adapt to the scale changes
\cite{liu2015real,akin2016deformable}. The sensitivity to fast motion
is generally handled in the long-term target tracking framework where
track reinilization module is triggered when the target is lost
\cite{ma2015long,de2015board,li2016monocular}.
\end{comment}

@@

\begin{figure}[!t]
\includegraphics[width=0.5\textwidth]{figures/Filters_Details.pdf}
\caption{The three filters called as medium ROI translation filter,
  target ROI scale filter and large ROI translation filter are
  shown. Also, the hanning window and desired Gaussian response for
  each filter are displayed.}
\label{fig:Filters}
\end{figure}

@@

\begin{algorithm}
	\caption{The MKCF Tracking Algorithm.}\label{alg:MKCF}
	\begin{algorithmic}[1]
	\State \textbf{Input} : Initial bounding box $x_{0}$, frame counter $fc$, scale filter frequency $n$,
	\State \textbf{Output} : 
				\If{$fc\:\%\:n=0$} \Comment{Condition 1}
						\State Estimated Target State $x_{t} = (x_{t-1},y_{t-1},s_{t})$,
						Scale filter (\textit{target-only}) model $R_{s}$.
			     \EndIf
				\If{$fc\:\%\:n=1$}\Comment{Condition 2}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t_1})$,
						Large Area Translation Filter model $R_{t}^{L}$.
				\EndIf
				\If{$fc\:\%\:n>1$}\Comment{Condition 3}
						\State Estimated Target State $x_{t} = (x_{t},y_{t},s_{t})$,
						Small Area Translation Filter model $R_{t}^{S}$.
				\EndIf
	\Procedure{track}{$x_{t-1},y_{t-1},s_{t-1}$} 
				\State // Translation Estimation
				\State Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $x_{t} = (x_{t},y_{t},s_{t-1})$;
				\State // Translation Estimation
				\State Crop the ROI for the $R_{t}^{L}$, or $R_{t}^{S}$ given $x_{t}$
				and estimate translation ($x_{t}$,$y_{t}$) using $R_{t}^{L}$ (Condition 2) or $R_{t}^{S}$ (Condition 3),
				\State Skip translation estimation for $R_{s}$ (Condition 1);
				\State // Scale Estimation
			    \State Crop the ROI for the $R_{s}$ and estimate scale, $s_{t}$, using $R_{s}$ (Condition 1) or $R_{t}^{S}$ (Condition 2), 
		         \State Skip it for $R_{t}^{L}$ (Condition 1),
				\State Scale pool for $R_{s}$ : $\lbrace1.05,1.0,1/1.05\rbrace$, and for $R_{t}^{S}$ : $\lbrace1.02,1.0,1/1.02\rbrace$;
				\State // Update Translation
				\State Perform Importance Re-sampling for Particle Filter and compute the mean of posterior pdf $x_{t} = (x_{t},y_{t},s_{t})$;
			    \State // Model Update
				\If{$max(y_{R_{s}}) \geq T_{R_{s}}$}
				\State Update $R_{s}$ (Condition 1);
				\EndIf							 
				\If{$max(y_{R_{t}^{L}}) \geq T_{R_{t}^{L}}$} 
				\State Update $R_{t}^{L}$ (Condition 2);
				\EndIf	
			     \If{$max(y_{R_{t}^{S}}) \geq T_{R_{t}^{S}}$}
				\State Update $R_{t}^{S}$ (Condition 3);
			     \EndIf		
	\EndProcedure	
	\end{algorithmic}
\end{algorithm}

@@

%----------------------------------------------------------------------
\section{Experiments} \label{sc:Experiments}
%---------------------------------------------------------------------- 
To verify the usefulness of our algorithm, we ran our algorithm using
three publicly available dataset:
VOT2015 \footnote{\url{http://www.votchallenge.net/}},
OTB100 \footnote{\url{http://cvlab.hanyang.ac.kr/tracker_benchmark/benchmark_v10.html}},
UAV123 \footnote{\url{https://ivul.kaust.edu.sa/Pages/Dataset-UAV123.aspx}}\cite{mueller2016uav123}.
